\subsection*{Digital Signal Processing Overall Project}

\#\+Dependancies\+: Open\+CV 3.\+0+

Install V\+Mware Ubuntu from S\+S\+P7. Request admin rights for VM.

Make sure you have internet access on the VM. If you don\textquotesingle{}t, call service IT (1300).

Run in terminal\+: {\bfseries sudo apt-\/get update}

{\bfseries sudo apt-\/get upgrade}

{\bfseries sudo apt-\/get install git}

{\bfseries sudo apt-\/get install codeblocks}

This will install the prebuilt Open\+CV library for Ubuntu (it is usually relatively old). It will be sufficient for now.

{\bfseries sudo apt-\/get install libopencv-\/dev python-\/opencv}

This step will be updated in time to install the latest Open\+CV library.

Create a \char`\"{}\+Work\char`\"{} directory on your VM. ({\bfseries mkdir Work}) Go to this folder ({\bfseries cd Work}) and run\+:

{\bfseries git clone --recurse-\/submodules \href{http://github.conti.de/uidg6179/DSP.git}{\tt http\+://github.\+conti.\+de/uidg6179/\+D\+S\+P.\+git}}

If you used \char`\"{}git clone\char`\"{}, just use the command \char`\"{}git submodule update -\/-\/init\char`\"{} afterwards.

After downloading all the files, open Code\+Blocks and select \char`\"{}\+Open existing project\char`\"{}. Select the project located in the \char`\"{}\+D\+S\+P/src\char`\"{} folder.

If everything went well, you should be able to build and run the code on your VM. Happy coding.

In order to make sure the repository is up to date with the main branch\+:

This will show you the differences between local repository and branch\+:

{\bfseries git status}

This will update your local repository with the commited versions from branch\+:

{\bfseries git pull --recurse-\/submodules}

In order to commit something in your submodule\+:

Create a local repository for your own submodule and after modifying the files\+:

(Optional)$\ast$$\ast$git status$\ast$$\ast$

{\bfseries git add} $\ast$

{\bfseries git commit -\/m \char`\"{}insert message\char`\"{}}

{\bfseries git push}

To update submodule versions in higher project\+:

{\bfseries cd submodule-\/name}

{\bfseries git checkout $<$tagname$>$}

{\bfseries cd ..}

{\bfseries git add submodule-\/name}

{\bfseries git commit -\/m \char`\"{}updating submodule to $<$tagname$>$\char`\"{}} 